---
title: 'Survey Results: Food, Animals, and Commons'
author: "Will Jones"
date: "March 26, 2015"
output:
  html_document:
    keep_md: yes
---

```{r, echo=FALSE, warning=FALSE}
suppressPackageStartupMessages(library(dplyr))
suppressPackageStartupMessages(library(magrittr))
suppressPackageStartupMessages(library(ggplot2))

data <- read.csv("commons_food_animals_clean.csv") %>% tbl_df()

attitude.labels <- c("Strongly disagree",
                     "Disagree",
                     "No opinion",
                     "Agree",
                     "Strongly Agree")

#data$commons.freq <-
#  factor(data$commons.freq, )

data$attitudes.env <- factor(data$attitudes.env,
    levels = 1:5, labels = attitude.labels, ordered = TRUE)
data$attitudes.killing <- factor(data$attitudes.killing,
    levels = 1:5, labels = attitude.labels, ordered = TRUE)
data$attitudes.products <- factor(data$attitudes.products,
    levels = 1:5, labels = attitude.labels, ordered = TRUE)
data$attitudes.veggie.health <- factor(data$attitudes.veggie.health,
    levels = 1:5, labels = attitude.labels, ordered = TRUE)
data$attitudes.vegan.health <- factor(data$attitudes.vegan.health,
    levels = 1:5, labels = attitude.labels, ordered = TRUE)
data$attitudes.protein <- factor(data$attitudes.protein,
    levels = 1:5, labels = attitude.labels, ordered = TRUE)
data$attitudes.culture <- factor(data$attitudes.culture,
    levels = 1:5, labels = attitude.labels, ordered = TRUE)

data$commons.veggie.good <- factor(data$commons.veggie.good,
    levels = 1:5, labels = attitude.labels, ordered = TRUE)
data$commons.vegan.good <- factor(data$commons.vegan.good,
    levels = 1:5, labels = attitude.labels, ordered = TRUE)
data$commons.vegan.consistent <- factor(data$commons.vegan.consistent,
    levels = 1:5, labels = attitude.labels, ordered = TRUE)
data$commons.veggie.consistent <- factor(data$commons.veggie.consistent,
    levels = 1:5, labels = attitude.labels, ordered = TRUE)
data$commons.respect <- factor(data$commons.respect,
    levels = 1:5, labels = attitude.labels, ordered = TRUE)

```

Over a couple weeks, the Quest and Greenboard have been collecting response for
a survey, asking students questions about their beliefs and choices about animals and food,
and whether and in what ways they believe Commons respects those beliefs and choices.

We have recieved 119 responses to our survey.

```{r, echo=FALSE}
# For the purposes of anaylsis, we are going to group some
# of the more unique responses with larger categories (i.e.
# interpret 'vegan straight edge' as fitting in with the 
# category of 'vegan'.)
data %<>%
  mutate(diet = as.character(diet),
    diet = ifelse(diet == "don't buy meat (eat it at the scrounge)", 
                       "I eat meat sparingly", diet),
         diet = ifelse(diet == "vegan straight edge",
                       "I am vegan", diet))

ggplot(data, aes(x = reorder(diet, diet, function(x)-length(x)) )) + 
  geom_bar() + 
  labs(title = "Diets of Survey Respondents",
       x = "Diet", y = "Count")


ggplot(data, aes(x = time.at.reed)) + geom_bar() + 
  labs(title = "Distribution of Class",
       x = "Time respondent has been at Reed, in semesters",
       y = "Count")

ggplot(data, aes(x = reorder(commons.freq, commons.freq, function(x)-length(x) ))) + 
  geom_bar() + 
  labs(title = "How often do they eat at Commons?",
       x = "Frequency of eating at Commons",
       y = "Count")


```

We have a decent number of people responding saying they are vegetarian, vegan, and regular
meat eaters. Those that eat meat sparingly are a little more sparse in our respondents, but
we definetly can't draw any meaningful conclusions about pescetarians or other diets given
their representation here.

We did seem to get a good distribution across different graduating years of Reedies.


## Attitudes and Beliefs About Animals and Food
```{r, echo=FALSE}
# When faceting across different diets, let's just examine the four main ones
main.diets <- c("I am vegetarian",
                "I am vegan",
                "I regularly eat meat",
                "I eat meat sparingly")
data.diets <-
  data %>%
  filter(diet %in% main.diets)

data.diets %>%
  ggplot(aes(x =  attitudes.env) ) + 
  geom_bar() + 
  facet_wrap(~diet) + 
  labs(title = "The mass production of meat posses a serious threat the environment.",
       x = "Agreement with statement",
       y = "Count")

summary(data$attitudes.env)
```

The majority of respondents, 108 or 92%, either agree or strongly agree that the 
mass production of meat posses a serious threat to the environment. Those that eat
meat regularly are less likely to strongly agree with this statement, as compared
with other diets, however.

```{r, echo=FALSE}
ggplot(data.diets, aes(x = attitudes.killing)) +
  geom_bar() + 
  facet_wrap(~diet) + 
  labs(title = "Killing animals in order to eat them is abusive.",
       x = "Level of Agreement")

ggplot(data.diets, aes(x = attitudes.products)) + 
  geom_bar() + 
  facet_wrap(~diet) + 
  labs(title = "Raising animals to harvest products, such as eggs or milk, is animal abuse.",
       x = "Level of Agreement")

ggplot(data.diets, aes(x = attitudes.veggie.health)) + 
  geom_bar() + 
  facet_wrap(~diet) +
  labs(title = "A diet without meat is healthier.",
       x = "Level of Agreement")

ggplot(data.diets, aes(x = attitudes.vegan.health)) + 
  geom_bar() + 
  facet_wrap(~diet) +
  labs(title = "A diet without animal products is healthier",
       x = "Level of Agreement")

ggplot(data.diets, aes(x = attitudes.protein)) + 
  geom_bar() + 
  facet_wrap(~diet) + 
  labs(title = "It is harder to consume enough protein without meat
       in one's diet.",
       x = "Level of Agreement")

ggplot(data.diets, aes(x = attitudes.culture)) + 
  geom_bar() + 
  facet_wrap(~diet) + 
  labs(title = "Eating meat is an important part of a culture I identify with.",
       x = "Level of Agreement")

```


## On Commons


```{r, echo=FALSE}
ggplot(data.diets, aes(x = commons.veggie.good)) + 
  geom_bar() + 
  facet_wrap(~diet) + 
  labs(title = "When Commons serves specials that are vegetarian,
       they are good",
       x = "Level of agreement")

ggplot(data.diets, aes(x = commons.vegan.good)) + 
  geom_bar() + 
  facet_wrap(~diet) +
  labs(title = "When Commons serves specials that are vegan,
       they are good.",
       x = "Level of Agreement")

ggplot(data.diets, aes(x = commons.veggie.consistent)) + 
  geom_bar() + 
  facet_wrap(~diet) + 
  labs(title = "Commons has vegetarian specials consistently.",
       x = "Level of Agreement")

ggplot(data.diets, aes(x = commons.vegan.consistent)) + 
  geom_bar() + 
  facet_wrap(~diet) + 
  labs(title = "Commons has vegan specials consistenyly.",
       x = "Level of agreement")

ggplot(data.diets, aes(x = commons.respect, fill = commons.freq)) + 
  geom_bar() + 
  facet_wrap(~diet) + 
  labs(title = "I feel that commons respects my beliefs about food and animals. ",
       x = "Level of Agreement")

ggplot(data.diets, aes(x = commons.pigday)) + 
  geom_bar() + 
  facet_wrap(~diet) + 
  labs(title = "I feel that commons respects my beliefs about food and animals. ",
       x = "Level of Agreement")

ggplot(data.diets, aes(x = diet, fill = commons.freq)) + 
  geom_bar() + 
  labs(title = "Frequency of eating at Commons, by diet",
       x = "Diet", y = "Frequency of eating at Commons")
```


```{r, echo=FALSE}
ggplot(data.diets, aes(x = commons.respect,
                       fill = commons.freq)) +
  geom_bar()

data %>%
  filter(diet == "I regularly eat meat") %>%
  .$commons.respect %>%
  summary()


```

