---
title: 'Survey Results: Food, Animals, and Commons'
author: "Will Jones"
date: "March 26, 2015"
output: html_document
---

```{r, echo=FALSE, warning=FALSE}
library(dplyr)
library(magrittr)
library(ggplot2)

data <- read.csv("commons_food_animals_clean.csv") %>% tbl_df()

attitude.labels <- c("Strongly disagree",
                     "Disagree",
                     "No opinion",
                     "Agree",
                     "Strongly Agree")


data$attitudes.env <- factor(data$attitudes.env,
    levels = 1:5, labels = attitude.labels, ordered = TRUE)
data$attitudes.killing <- factor(data$attitudes.killing,
    levels = 1:5, labels = attitude.labels, ordered = TRUE)
data$attitudes.products <- factor(data$attitudes.products,
    levels = 1:5, labels = attitude.labels, ordered = TRUE)
data$attitudes.veggie.health <- factor(data$attitudes.veggie.health,
    levels = 1:5, labels = attitude.labels, ordered = TRUE)
data$attitudes.vegan.health <- factor(data$attitudes.vegan.health,
    levels = 1:5, labels = attitude.labels, ordered = TRUE)
data$attitudes.protein <- factor(data$attitudes.protein,
    levels = 1:5, labels = attitude.labels, ordered = TRUE)
data$attitudes.culture <- factor(data$attitudes.culture,
    levels = 1:5, labels = attitude.labels, ordered = TRUE)

data$commons.veggie.good <- factor(data$commons.veggie.good,
    levels = 1:5, labels = attitude.labels, ordered = TRUE)
data$commons.vegan.good <- factor(data$commons.vegan.good,
    levels = 1:5, labels = attitude.labels, ordered = TRUE)
data$commons.vegan.consistent <- factor(data$commons.vegan.consistent,
    levels = 1:5, labels = attitude.labels, ordered = TRUE)
data$commons.veggie.consistent <- factor(data$commons.veggie.consistent,
    levels = 1:5, labels = attitude.labels, ordered = TRUE)
data$commons.respect <- factor(data$commons.respect,
    levels = 1:5, labels = attitude.labels, ordered = TRUE)

```

Over a couple weeks, the Quest and Greenboard have been collecting response for
a survey, asking students questions about their beliefs and choices about animals and food,
and whether and in what ways they believe Commons respects those beliefs and choices.

We have recieved 117 responses to our survey.

```{r, echo=FALSE}
# For the purposes of anaylsis, we are going to group some
# of the more unique responses with larger categories (i.e.
# interpret 'vegan straight edge' as fitting in with the 
# category of 'vegan'.)
data %<>%
  mutate(diet = as.character(diet),
    diet = ifelse(diet == "don't buy meat (eat it at the scrounge)", 
                       "I eat meat sparingly", diet),
         diet = ifelse(diet == "vegan straight edge",
                       "I am vegan", diet))

ggplot(data, aes(x = reorder(diet, diet, function(x)-length(x)) )) + 
  geom_bar() + 
  labs(title = "Diets of Survey Respondents",
       x = "Diet", y = "Count")

ggplot(data, aes(x = time.at.reed)) + geom_bar() + 
  labs(title = "Distribution of Class",
       x = "Time respondent has been at Reed, in semesters",
       y = "Count")

ggplot(data, aes(x = reorder(commons.freq, commons.freq, function(x)-length(x) ))) + 
  geom_bar() + 
  labs(title = "How often do they eat at Commons?",
       x = "Frequency of eating at Commons",
       y = "Count")


```

We have a decent number of people responding saying they are vegetarian, vegan, and regular
meat eaters. Those that eat meat sparingly are a little more sparse in our respondents, but
we definetly can't draw any meaningful conclusions about pescetarians or other diets given
their representation here.

We did seem to get a good distribution across different graduating years of Reedies.


## Attitudes and Beliefs About Animals and Food
```{r, echo=FALSE}
# When faceting across different diets, let's just examine the four main ones
main.diets <- c("I am vegetarian",
                "I am vegan",
                "I regularly eat meat",
                "I eat meat sparingly")
data.diets <-
  data %>%
  filter(diet %in% main.diets)

data.diets %>%
  ggplot(aes(x =  attitudes.env) ) + 
  geom_bar() + 
  facet_wrap(~diet) + 
  labs(title = "The mass production of meat posses a serious threat the environment.",
       x = "Agreement with statement",
       y = "Count")

summary(data$attitudes.env)
```

The majority of respondents, 108 or 92%, either agree or strongly agree that the 
mass production of meat posses a serious threat to the environment. Those that eat
meat regularly are less likely to strongly agree with this statement, as compared
with other diets, however.

```{r, echo=FALSE}
ggplot(data.diets, aes(x = attitudes.killing)) +
  geom_bar() + 
  facet_wrap(~diet)

ggplot(data.diets, aes(x = attitudes.products)) + 
  geom_bar() + 
  facet_wrap(~diet)

ggplot(data.diets, aes(x = attitudes.veggie.health)) + 
  geom_bar() + 
  facet_wrap(~diet)

ggplot(data.diets, aes(x = attitudes.vegan.health)) + 
  geom_bar() + 
  facet_wrap(~diet)

ggplot(data.diets, aes(x = attitudes.protein)) + 
  geom_bar() + 
  facet_wrap(~diet)

ggplot(data.diets, aes(x = attitudes.culture)) + 
  geom_bar() + 
  facet_wrap(~diet)
```


## On Commons


```{r, echo=FALSE}
ggplot(data.diets, aes(x = commons.veggie.good)) + 
  geom_bar() + 
  facet_wrap(~diet)

ggplot(data.diets, aes(x = commons.vegan.good)) + 
  geom_bar() + 
  facet_wrap(~diet)

ggplot(data.diets, aes(x = commons.veggie.consistent)) + 
  geom_bar() + 
  facet_wrap(~diet)

ggplot(data.diets, aes(x = commons.vegan.consistent)) + 
  geom_bar() + 
  facet_wrap(~diet)

ggplot(data.diets, aes(x = commons.respect)) + 
  geom_bar() + 
  facet_wrap(~diet)

ggplot(data.diets, aes(x = diet, fill = commons.freq)) + 
  geom_bar()
```


